%% ==================
\chapter{Results}
\label{ch:results}
%% ==================
%
%My results:

\section{Recreating previous results}
%	-Only 3 original components
%		-Spherical excess
%		-very bad chi2 in disk and bubbles

\todo{picture of GC excess, maybe comparison with previous papers.}
I was able to recreate a more or less spherical excess in GC around 2GeV.\\
Bad fit in disk and bubbles as expected.
Two problems :
\begin{itemize}
\item Spectrum too hard at high energies
\item Excess around 2GeV
\end{itemize}

\todo{picture of weniger plots}
Introduce the weniger plots here (or in the state of the research?) to show excess in GC.

\section{? Introducing SCR ?}


\section{Introducing SCR and MCR}
%	-Introduction of SCR and MCR
%		-very good chi2 in disk and bubbles
%		-spatial shapes of comps
%			-IC sperical (as expected) but depletion in disk
%			-BR low in bubbles replaces IC in disk
%			-PCR OK but low in disk
%			-MCR follows CO map, take place of PCR in disk
%			-SCR follows bubble structure

\todo{pictures of chi2. }
First obvious thing is the good chi2 in the disk and bubbles. SCR takes care of high energies, MCR of the 2GeV excess.\\

\subsection{Discussion on spatial shapes}
\todo{pictures of the spatial distributiions. MAybe on a page.}
IC is more or less spherical as expected (starlight). There is a disturbing sandwich structure!
BR is consitent with what is expected.
PCR looks OK too, but has the same sandwich structure as IC. Maybe MCR takes too much space in the disk, or proton spectrum is not perfectly correct.
MCR follows very well a gas map (traced by CO).
SCR draws almost perfectly the disk and bubbles as expected.


\section{Introducing SCR and DM}
%	-Introduction of SCR + DM
%		-chi2
%		-spatial shapes	
%		-Weniger plots
%		-Specklings
\todo{include spectrum of best mass DM fitted in CMZ. Also pictures of DM distribution compared to gas map.}
Determination of best WIMP mass around 50GeV in CMZ.
DM shape follows the gas map too (like MCR). That does not make any sense.



\section{Introducing SCR and MSP}
%	-Introduction of SCR + MSP:
%		-chi2
%		-spatial shapes
%		-Weniger plots
%		-Specklings

\todo{pictures of MSP spectrum, chi2. Residuals at low energy maybe?}
Bad chi2 compared to MCR. The low energy spectrum is too hard.






